Recipient plant traits are important determinants of the impacts of heterospecific pollen upon plant reproduction

### 2019-03-15 Manuscript_draft/Manuscript_draft.Rmd
EDITS GGPLOTS

affiliation:
- affil: University of New England (Australia)
  affilnum: 1
- affil: Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain
  affilnum: 2
- affil: Department of Biological Sciences, University of Pittsburgh 4249 Fifth Avenue, Pittsburgh, Pennsylvania 15260-3929 USA
  affilnum: 3
output:
  pdf_document:
    fig_caption: yes
    fig_height: 7
    fig_width: 7
    includes:
      in_header: header.tex
    keep_tex: yes
    number_sections: no
    template: manuscript.latex
  word_document: null
  html_document: null
capsize: normalsize
classoption: a4paper
csl: ecology.csl
documentclass: article
fontsize: 11pt
footerdate: yes
geometry: margin=1in
linenumbers: yes
bibliography:
- references.bib
- knitcitations.bib
spacing: doublespacing
abstract: no
---

@@

\newpage
```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE,fig.height=4,fig.width=7, fig.cap="Barplot with the different treatments that provide information of the reproductive biology of the ten species. The y axis is the proportion of ovules converted to seed in percentage. The different treatments (N=10) which are presented in the legend are, hand cross-pollination, hand self-pollination, natural selfing and apomixis. More information about these treatments can be found in Methods and Appendices."}

load("r_biology.RData")

ggplot(bio,aes(x=Species,y=value,fill=variable))+
  geom_bar(stat="identity",position="dodge")+scale_fill_grey(start = 0, end = 0.85,name="Treatments") + 
  theme_minimal()+xlab("Species")+ylab("Seed-setting rate (%)")+labs(title="Reproductive biology test")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, face= "italic",family = ""), legend.text=element_text(size=7), legend.title=element_text(size=8), axis.text.y  = element_text(size = 10))+
  scale_y_continuous(minor_breaks = seq(0 , 100, 5), breaks = seq(0, 100, 10))

@@

@@

<div id = "refs"></div>

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
load("pollen_ratio.RData")

ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="A) Brassicaceae") +
  theme(axis.text.x=element_text(angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
  geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")

ggplot(pollen_ratios_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="B) Solanaceae") +
  theme(axis.text.x=element_text(angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
  geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")

ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="C) Convolvulaceae") +
  theme(axis.text.x=element_text(angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
  geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")

>>>>

affiliation:
- affil: University of New England (Australia)
  affilnum: 1
- affil: Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain
  affilnum: 2
- affil: Department of Biological Sciences, University of Pittsburgh 4249 Fifth Avenue, Pittsburgh, Pennsylvania 15260-3929 USA
  affilnum: 3
output:
  pdf_document:
    fig_caption: yes
    fig_height: 7
    fig_width: 7
    includes:
      in_header: header.tex
    keep_tex: yes
    number_sections: no
    template: manuscript.latex
  word_document: null
  html_document: null
capsize: normalsize
classoption: a4paper
csl: ecology.csl
documentclass: article
fontsize: 11pt
header-includes: \usepackage{float}
footerdate: yes
geometry: margin=1in
linenumbers: yes
bibliography:
- references.bib
- knitcitations.bib
spacing: doublespacing
abstract: no
---
```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'h')
```

@@

\newpage
```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE,fig.height=4,fig.width=7, fig.cap="Barplot with the different treatments that provide information of the reproductive biology of the ten species. The y axis is the proportion of ovules converted to seed in percentage. The different treatments (N=10) which are presented in the legend are, hand cross-pollination, hand self-pollination, natural selfing and apomixis. More information about these treatments can be found in Methods and Appendices."}
load("r_biology.RData")
library(ggpubr)
library(cowplot)
library(gridExtra)
library(egg)
library(magrittr)
library(multipanelfigure)
library(grid)
ggplot(bio,aes(x=Species,y=value,fill=variable))+
  geom_bar(stat="identity",position="dodge")+scale_fill_grey(start = 0, end = 0.85,name="Treatments") + 
  theme_minimal()+xlab("Species")+ylab("Seed-setting rate (%)")+labs(title="Reproductive biology test")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, face= "italic",family = ""), legend.text=element_text(size=7), legend.title=element_text(size=8), axis.text.y  = element_text(size = 10))+
  scale_y_continuous(minor_breaks = seq(0 , 100, 5), breaks = seq(0, 100, 10))

@@

```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE, fig.height=3,fig.width=5,fig.cap="a"}
load("Data/family_cor.RData")
library(ggpubr)
library(ggplot2)
library(gridExtra)
library(grid)

p1 <- ggscatter(sola, x = "Cohen_d", y = "style_length", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Hedges' g", ylab = "Style length (mm)", main="A) Solanaceae")

p2<- ggscatter(a, x = "Cohen_d", y = "style_length", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Hedges' g", ylab = "Style length (mm)", main="A) All families")
grid.arrange(p1, p2, nrow = 1, ncol=2)

I haven't add this to the draft yet but when I look just Solanaceae species, interestingly seems to be a negative trend with style length and heterospecific pollen effect. Curiously, Capsicum and tomato are the ones that are more affected by hp and both have the shortest stigma and style.
The stigma results of tomato are supported by the plot of effct sizes per family where convolvulaceae has a greater negative effect than the other two families (and they are the ones with bigger pollen size)

Here I show the plot of just solanaceae and then with all the species. I have gouped all the treatments, if not I feel like we are doing p hacking with all the analysis, because is increasing the strength of each point 9 times.

@@

<div id = "refs"></div>
\newpage

@@

```{r, echo=FALSE, message=FALSE,fig.height=10,fig.width=5, warning=FALSE,fig.cap="Pollen ratios separated by family A) Brassicaceae, B) Solanaceae, C) Convolvulaceae. Pollen was counted for crosses with species of the other two families (N=3). To prepare these ratios all the pollen grains on the stigma were counted.", cache=FALSE}
load("pollen_ratio.RData")
library(ggpubr)
library(ggplot2)
library(gridExtra)
library(grid)

p1 <- ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="A) Brassicaceae") +
  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
  geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")

p2 <- ggplot(pollen_ratios_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="B) Solanaceae") +
  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
  geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")

p3 <-ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="C) Convolvulaceae") +
  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
  geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")
grid.arrange(p1, p2,p3, nrow = 3, ncol=1)
